### 2014-03-28 brains-results.tex
Add a mising question to be addressed
Move figures around, and create one page of figures per feature

\begin{figure*}[!th]
	\centering
	\subfloat[][Age-of-Acquisition]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_aoa-Kuperman-all_suscept.png}
		\label{fig:aoa-suscept}
	}
	~
	\subfloat[][Number of phonemes]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_cmu-MNphonemes-all_suscept.png}
		\label{fig:MNphonemes-suscept}
	}
	\caption{Susceptibility values in color over the histograms of feature values}
\end{figure*}

\begin{figure*}[!th]
	\centering
	\subfloat[][Age-of-Acquisition]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_aoa-Kuperman-all_absolute.png}
		\label{fig:aoa-absolute}
	}
	~
	\subfloat[][Number of phonemes]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_cmu-MNphonemes-all_absolute.png}
		\label{fig:MNphonemes-absolute}
	}
	\caption{Variations of features, with corresponding values under $\mathcal{H}_0$ and $\mathcal{H}_{0,n}$}
\end{figure*}

@@

\begin{figure*}[!th]
	\centering
	\subfloat[][Log PageRank]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-PR_scores-all_absolute.png}
		\label{fig:PR_scores-absolute}
	}
	~
	\subfloat[][Log Betweenness coefficient]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-BCs-all_absolute.png}
		\label{fig:BCs-absolute}
	}
	~
	\subfloat[][Log Clustering coefficient]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-CCs-all_absolute.png}
		\label{fig:CCs-absolute}
	}
	\caption{Variations of features, with corresponding values under $\mathcal{H}_0$ and $\mathcal{H}_{0,n}$}
\end{figure*}

@@

\begin{figure*}[!th]
	\centering
	\subfloat[][Log PageRank]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-PR_scores-all_suscept.png}
		\label{fig:PR_scores-suscept}
	}
	~
	\subfloat[][Log Betweenness coefficient]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-BCs-all_suscept.png}
		\label{fig:BCs-suscept}
	}
	~
	\subfloat[][Log Clustering coefficient]{
		\includegraphics[width=0.3\textwidth]{images/Fff_Mtbgs_Sno_Pall_N5_fa-CCs-all_suscept.png}
		\label{fig:CCs-suscept}
	}
	\caption{Susceptibility values in color over the histograms of feature values}
\end{figure*}

%\begin{figure}[!th]
%\includegraphics[width=\linewidth]{algorithms/Rplot.pdf}
%\end{figure}

>>>>

@@

@@

\rk{A big question to be addressed is the ``why'': what underlying aspect of words with these features make them words to be substituted or not, and why does the brain do that? How was that selected for in evolution?}
